From physical principles to ???

### 2016-02-16 2015CompleteDerivation/completeDerivation.tex
Finished annotating state section with all open issues

\begin{defn}\label{detrevmap}
A deterministic and reversible evolution is a bijective map $f_{\Delta t}:\mathcal{S} \leftrightarrow \mathcal{S}$ on the state space.
\end{defn}

\begin{justification}
The system is deterministic: there exists a map $f:\mathcal{S} \rightarrow \mathcal{S}$ that returns the final state given the initial state. The system is reversible: there exists a map $g:\mathcal{S} \rightarrow \mathcal{S}$ that returns the initial state given the final state. $g \circ f = id$ as mapping forward and then backward must return the original element.
\end{justification}

@@

@@

\begin{prop}\label{evolved variable}
TODO: Define and prove existence
\end{prop}

\begin{prop}\label{transported variable}
TODO: Define and prove existence
\end{prop}

@@

>>>>

TODO: det/rev map from manifold to manifold. Must be physically distinguishable. Can't be the whole class of functions: refining domain does not refine codomain. (mathematically, cardinality greater than continuoum, i.e. not second countable) We need that arbitrarily refining domain refines the codomain. Equivalent to continuous function(?). OR Measurement/process outcomes from initial states corresponds to outcomes on final states. That is: we map open sets to open sets.

\begin{defn}\label{detrevmap}
A deterministic and reversible evolution is a self-homeomorphism on the state space $\mathcal{S}$.
\end{defn}

\begin{justification}
The system is deterministic: there exists a map $f:\mathcal{S} \rightarrow \mathcal{S}$ that returns the final state given the initial state. The system is reversible: there exists a map $g:\mathcal{S} \rightarrow \mathcal{S}$ that returns the initial state given the final state. $g \circ f = id$ as mapping forward and then backward must return the original element.

TODO: show it maps open sets to open sets.
\end{justification}

@@

TODO: maybe best to define state vector directly, and state variables as part of state vector? Define discrete state variable when co-domain is integers and define continuous state variable when co-domain is real? Can we prove a state vector always exists, of real variables? For discrete topology, we should always be able to do it. In general, state vector defines charts, so we should not have a single chart for the whole state space. What does it mean physically? Does it matter?

@@

\begin{defn}\label{evolved_transported_variable}
TODO: Define evolved and transported variables in terms of pushback/pushforward
\end{defn}

\begin{justification}
TODO: prove existence
\end{justification}

@@

TODO: in continuous, not necessarily the Cartesian product. But we can always create a chart with state variables. State space is a manifold of dimension n. In principle, we could say more. For example, a deterministic/reversible map would not map a set to its subset or superset. We could define a metric, this would give us an ergotic system. Not going to do that.
